---
title: 'Assignment A02: TIDYVERSE'
author: R package build
date: '2021-05-26'
slug: assignment-a02-tidyverse
categories:
  - Tidyverse
tags: []
output:
   html_document:
     code_folding: show
---
For using one table verb functions,I have chosen heart failure clinical records dataset. Heart failure is a common event caused by CVDs and this dataset contains 12 features that can be used to predict mortality by heart failure. I have applied two functions only here.
```{r warning=FALSE, message=FALSE, class.source = 'fold-show'}
library(tidyverse)
heartdisease <- read_csv("heart_failure_clinical_records_dataset.csv")
#head(heart_failure_clinical_records_dataset)
head(heartdisease)
```
## One table verb functions
```{r warning=FALSE, message=FALSE, class.source = 'fold-show'}
heartdisease %>%
filter(diabetes == 1, age >= 50) %>%
arrange(desc(serum_creatinine)) %>%
  select(diabetes, age, serum_creatinine)
```
## two table verb functions
For using two table functions, I have use world happiness dataset for the year 2015 and 2016.The World Happiness Report is a landmark survey of the state of global happiness.This data set contains following columns: Country,Region, Happiness Rank, Happiness Score, GDP per Capita, Family, Life Expectancy, Freedom, Generosity, Trust(Government Corruption), Generosity, Dystopia Residual etc.
```{r warning=FALSE, message=FALSE, class.source = 'fold-show'}
library(tidyverse)
library(dplyr)
library(ggplot2)
library(repr)
library(tidyr)
x15 <- read_csv("2015.csv")
x16 <- read_csv("2016.csv")
head(x15)
head(x16)
left_joined <- left_join(x15, x16, by = c("Country"))
right_joined <- right_join(x15, x16, by = c("Country"))
inner_joined <- inner_join(x15, x16, by = c("Country"))
```
## Grouping functions 
```{r warning=FALSE, message=FALSE, class.source = 'fold-show'}
Group <- heartdisease %>%
group_by(age) %>%
  summarise(mean_creatinine = mean(serum_creatinine))
Group
```
## rowwise Grouping function
```{r warning=FALSE, message=FALSE, class.source = 'fold-show'}
heartdisease %>% 
  rowwise() %>% 
  mutate(m = min(c(high_blood_pressure, smoking)))
```
## Vector functions 
```{r warning=FALSE, message=FALSE, class.source = 'fold-show'}
filter(heartdisease, between(age, 50, 70))
heartdisease %>% arrange(desc(time))
```
## Pivoting function 
```{r warning=FALSE, message=FALSE, class.source = 'fold-show'}
library(tidyr)
x15 %>%
pivot_longer(cols = c('Country', 'Region'), names_to = "A", values_to = "B")
```
## Pivoting function
```{r warning=FALSE, message=FALSE, class.source = 'fold-show'}
library(tidyr)
heartdisease %>%
pivot_wider(names_from = diabetes, values_from = ejection_fraction)
```
## Missing Value function
```{r warning=FALSE, message=FALSE, class.source = 'fold-show'}
heartdisease %>%
  drop_na()
```
## Missing Value function
```{r warning=FALSE, message=FALSE, class.source = 'fold-show'}
heartdisease %>%
 fill(sex)
```
## Narrative 
I have found both the datasets, heart failure clinical records dataset and happiness dataset of Kaggle interesting. I hope to learn more to analyze how these datasets are meaningful by the end of this course. While doing this assignment of Tidyverse, I have found the Group_by functions of grouping most interesting compared to other functions.
